paper_replication

### 2021-12-15 paper_replication.Rmd
TODO list update

---
title: "paper_replication"
output: pdf_document
---
REPLICATION:
TODO: averages of averages vs. averages for table 2
TODO: the paper says "all models included state and year fixed effects and standard errors adjusted for state-level clustering" -> does this mean we need to include states as a variable in our model?
TODO: the paper says "We addressed data gaps in demographic variables by using the estimate from the nearest year for which an estimate was available", so we need to include this methodology
TODO: bias analysis as done in the paper, comparing Guttmacher Census State Data to our State Data
TODO: run the models without the distance variable as well as with the distance variable as the outcome, as done in the paper
TODO: write up everything: we need to follow the format of the original paper <- Toby
TODO: find abortion data used by Brown et al. to compare in discussion <- Toby

>>>>

---
title: "paper_replication"
output: pdf_document
---
REPLICATION:
TODO: averages of averages vs. averages for table 2

TODO: the paper says "all models included state and year fixed effects and standard errors adjusted for state-level clustering" -> does this mean we need to include states as a variable in our model?
-- No, they did that because they were doing the longitudinal analysis, so like abortion rates in a given state for one year are not independent of the next, so they're accounting for that.

TODO: the paper says "We addressed data gaps in demographic variables by using the estimate from the nearest year for which an estimate was available", so we need to include this methodology
TODO: bias analysis as done in the paper, comparing Guttmacher Census State Data to our State Data
TODO: run the models without the distance variable as well as with the distance variable as the outcome, as done in the paper
TODO: write up everything: we need to follow the format of the original paper <- Toby
TODO: find abortion data used by Brown et al. to compare in discussion <- Toby
